### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@b73a0f667deef12e815dc9d6d434575272fd86b3 🚀

\hypertarget{host-landscapes-generate-a-coevolutionary-mosaic}{%
\subsection{Host landscapes generate a coevolutionary
mosaic}\label{host-landscapes-generate-a-coevolutionary-mosaic}}

>>>>

\hypertarget{coevolutionary-regimes-structure-evolutionary-risk-of-zoonotic-emergence}{%
\subsection{Coevolutionary regimes structure evolutionary risk of
zoonotic
emergence}\label{coevolutionary-regimes-structure-evolutionary-risk-of-zoonotic-emergence}}
